\documentclass{article}
\usepackage[a4paper, margin=2cm, landscape]{geometry}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{fontenc}
\usepackage[utf8]{inputenc}

\begin{document}

\begin{center}
{\Large \textbf{Poster Presenters --- CompQMB2026}}
\end{center}

\vspace{1em}

\begin{longtable}{clp{4.5cm}p{3cm}p{8cm}}
\toprule
\textbf{\#} & \textbf{Name} & \textbf{Affiliation} & \textbf{Core time} & \textbf{Presentation Title} \\
\midrule
\endfirsthead
\toprule
\textbf{\#} & \textbf{Name} & \textbf{Affiliation} & \textbf{Core time} & \textbf{Presentation Title} \\
\midrule
\endhead
\bottomrule
\endfoot
1  & Lucas Arenstein     & University of Copenhagen & Mar. 4 & Full Grid Solution for Multi-Asset Options Pricing with Tensor Networks \\[4pt]
2  & Sanghyun Park       & Seoul National University & Mar. 3 & --- \\[4pt]
3  & Sung-Bin B. Lee     & Seoul National University & Mar. 4 & Strong simulation of two-dimensional instantaneous quantum polynomial-time circuits using tensor networks \\[4pt]
4  & Kiyeon Kim          & Seoul National University & Mar. 3 & Clebsch--Gordan coefficients without floating-point error: toward a non-Abelian-symmetric tensor library \\[4pt]
5  & Hirone Ishida       & Saitama University & Mar. 4 & Tensor rank optimization via variable transformation based on flow generative models \\[4pt]
6  & Tomoya Shiota       & The University of Osaka & Mar. 3 & --- \\[4pt]
7  & Yuichiro Yoshida    & The University of Osaka & Mar. 4 & Seniority zero-based strategy for doubling the size of quantum-selected configuration interaction and its application to QC-QSCI-AFQMC \\[4pt]
8 & Naoya Kuroda        & Center for Quantum Information and Quantum Biology, Osaka University & Mar. 3 & --- \\[4pt]
9 & Takuya Matsumoto    & Tohoku University & Mar. 4 & DMFT study for electron correlation effects on topological transport properties \\[4pt]
10 & Myungseok Nam       & Seoul National University & Mar. 3 & Solving finite-difference parquet equations for the Anderson model using quantics tensor trains \\[4pt]
11 & Kyungmin Yu         & Seoul National University & Mar. 4 & Dynamical Mean-Field Theory Study of Nagaoka Ferromagnetism in the Hubbard Model \\[4pt]
12 & Shuta Matsuura      & The University of Tokyo & Mar. 3 & Tensor cross interpolation approach for the quantum impurity problems based on the weak-coupling expansion \\[4pt]
13 & Tatsuya Yokota      & Nagoya Institute of Technology & Mar. 4 & Plug-and-Play Algorithms for Optimizing Tensor Networks in Machine Learning Problems \\[4pt]
14 & Do Tuan Minh        & The University of Osaka, QIQB & Mar. 3 & Tensor-train-based methods for optimizing high-entropy alloy nanoparticles \\[4pt]
15 & Masataka Yamamoto   & Nagoya Institute of Technology & Mar. 4 & An Automated Framework with Optimization Algorithms for Tensor Network Machine Learning \\[4pt]
16 & Natsuki Okada       & Chiba University & Mar. 3 & Field-induced phonon angular momentum across the superconducting transition in fullerides \\[4pt]
17 & Yuki Yamamoto       & The University of Osaka & Mar. 4 & Geometric Approach Based on Lattice Structure to Anomalous Many-Body Effects in 8-fold Quasicrystals \\[4pt]
18 & Guang Lin           & RIKEN AIP & Mar. 3 & Quantum data encoding for quantum machine learning \\[4pt]
19 & Haonan Huang        & RIKEN AIP & Mar. 4 & Multi-view Learning \\[4pt]
20 & Jian Xu             & RIKEN AIP & Mar. 3 & --- \\[4pt]
21 & Kota Ido            & ISSP & Mar. 4 & Software development for constructing ab initio effective Hamiltonians based on Wannier functions \\[4pt]
22 & Fu-Jiun Jiang       & Physics Department, National Taiwan Normal University & Mar. 3 & A machine learning study of both the two-dimensional antiferromagnetic and ferromagnetic Potts models on the square lattice \\[4pt]
23 & Xu Jian             & RIKEN AIP & Mar. 4 & --- \\[4pt]
24 & Hajime Miyamoto     & Center for Quantum Information and Quantum Biology, Osaka University & Mar. 3 & --- \\[4pt]
25 & Ryosuke Akashi      & National Institutes for Quantum Science and Technology & Mar. 4 & GW0-Eliashberg theory for phonon-and-plasmon-mediated superconductors using the intermediate representation \\[4pt]
\end{longtable}

\end{document}
